\section{Introduction}

Language models solve many arithmetic problems yet fail on superficially trivial
variants. A recurring explanation is that some intermediate value is computed but not
propagated, tested by probing the residual stream: if the value decodes, the model
``knows'' it. We show this inference is unsafe. A decodable value at the answer position
can be an operand-reconstructible, causally inert shadow of the computation, not the
computation itself.

Our vehicle is a single controlled failure. For $B, C \in [20,49]$, wrapping the first operand
in an additive identity, $(\,0 + B\,) * C =$, collapses accuracy to $0.27$ (instruct) / $0.51$
(base) although the model returns $B$ for $(\,0 + B\,) =$ at $1.00$ and multiplies inside a
bracket, $(\,B * C\,) =$, at $0.91$; the gap is large and tight
($\Delta(\text{C4}{-}\text{C1}) = 0.64$, $95\%$ CI $[0.60, 0.69]$, instruct). This is a clean
hook, not our contribution: we use it to ask whether a decodable representation at the answer
site licenses a claim about computation. Both $B$ and the product \bc{} are linearly decodable
there ($R^2 \approx 0.96$), inviting the reading that the product ``is represented but not
used.'' Figure~\ref{fig:hero} summarizes why that reading fails.

\input{sections/fig1_hero}

\paragraph{Contributions.}
\begin{itemize}[topsep=2pt,itemsep=1pt,leftmargin=1.2em]
\item A token-matched, control-rich instance of a compositional arithmetic blind spot
in Llama-3.1-8B: operation-specific, depth-sensitive, magnitude-controlled, and
few-shot-recoverable, each with a confidence interval (\S\ref{sec:blindspot}).
\item Evidence that the decodable answer-site subspace is \emph{operand-dominated}:
it has no margin over a linear-$(B,C)$ baseline where the band leaves no headroom, and
only a small margin (gap $\approx 0.06$, CI excludes zero) where it does, robust to a
pre-registered probe layer (\S\ref{sec:dormant}).
\item A causal test showing the decodable direction is \emph{inert}: probe-direction
steering and a full-residual swap at the answer position both leave the output unchanged,
anchored by a positive control (the same-family patching moves the answer at the operand
positions, recovery $0.50$), so the null is a dead site, not a dead probe. Within the swap's
small sub-flip effect, $\approx 85\%$ of the variance is orthogonal to the decode direction
(\S\ref{sec:dormant}).
\item A cross-family replication in matched bare format, together with an explicit
prompt-format confound that we argue precludes reading the cross-model results as a
clean family dissociation (\S\ref{sec:generality}).
\end{itemize}

We read the answer-site subspace as \emph{dormant} in the sense of
\citet{makelov-etal-2024-subspace}: present to a probe, invisible to the computation.
