\section{Related Work}
\label{sec:related}

\paragraph{Surface form and mathematical brittleness.}
Model math accuracy is sensitive to surface structure that leaves the answer invariant.
\citet{williamson-etal-2025-syntactic}, at the same venue, characterize a behavioral blind spot
in natural-language word problems where failure tracks dependency-locality complexity and
recovers under structure-lowering rephrasing, and conjecture a coupling between surface form and
internal representation. Our instance is orthogonal on both axes and \emph{tests} that
conjecture: a token-matched \emph{symbolic} expression whose additive-identity wrapper carries no
dependency-locality cost, for which we show the obvious representational reading (a
computed-but-unused product at the answer site) does not hold; the internal signature is a
dormant, operand-explained subspace, not a missing representation. \citet{reusch-lehner-2022-extracting}
show operator-tree structure is decodable from embeddings; we show that answer-site decodability
of the arithmetic \emph{value} can be an operand-reconstructible artifact that is causally inert,
so decodability of arithmetic structure does not certify its use.

\paragraph{Decodability versus causal use.}
A linear probe measures correlation, not use \citep{belinkov-2022-probing}, and can succeed on
random labels without a control \citep{hewitt-liang-2019-designing}. The sharpest form is the
subspace-patching illusion of \citet{makelov-etal-2024-subspace}: a direction can carry a
decodable signal yet be causally disconnected from the output. Our result is an arithmetic
instance of this illusion, established with a baseline and a steering test rather than assumed.
\citet{matsumoto-etal-2022-tracing} find decoded intermediate values in neural math solvers to
be causally usable; we find a decodable answer-site subspace that is causally inert. The results
are compatible: whether a decodable value is used is a per-site empirical question.

\paragraph{Mechanisms of arithmetic.}
\citet{stolfo-etal-2023-mechanistic} trace arithmetic from operand tokens to the final position
through late modules, and \citet{nikankin-etal-2025-arithmetic} argue models use a diffuse ``bag
of heuristics.'' Our localization agrees, and adds that the decodable answer-site value, easily
mistaken for the computed result, is a byproduct of that operand information. For method we
follow patching best practice \citep{zhang-nanda-2024-towards, heimersheim-nanda-2024-use}:
symmetric counterfactuals, a full-answer log-probability metric, and a positive control per null.
