\section{Setup and Research Questions}
\label{sec:setup}

\paragraph{Model and stimuli.}
We study Llama-3.1-8B \citep{grattafiori-etal-2024-llama}, base and instruction-tuned, in bare
continuation format, by greedy decoding and integer parsing. Stimuli are $N = 400$ operand pairs
$(B, C)$ drawn once with a fixed seed from $[20, 49]$ and held constant across every condition,
token-length matched, with spacing controlled. The central contrast is
$\text{C1} = (\,0 + B\,) * C =$ (the composed failure) against $\text{C4} = (\,B * C\,) =$
(multiply inside a bracket, succeeds) and $\text{C6} = (\,0 + B\,) =$ (evaluate the wrapper,
succeeds).

\paragraph{Metrics.}
Accuracies carry Wilson intervals; paired contrasts carry paired bootstrap intervals
(10{,}000 resamples). Decodability is five-fold cross-validated ridge $R^2$ (item-bootstrap
interval; selectivity-gap CIs use 300 resamples given the per-draw cross-validation cost) at a
named token position. Selectivity compares the decode against a linear-$(B,C)$
baseline (a probe given only the raw operands and Gaussian noise), so a high $R^2$ that is
merely linear in the operands does not count as representing the product. Causal tests use
symmetric operand counterfactuals and a full-answer log-probability metric
$\Delta = \log p(P') - \log p(\text{true})$; because Llama chunks the leading digits, a
first-token score is non-discriminative between two products.

\paragraph{Research questions.} \textbf{RQ1}: is the composition failure a genuine, controlled
effect or an artifact of difficulty, magnitude, or elicitation (\S\ref{sec:blindspot})?
\textbf{RQ2}: is the near-product decodable at the answer site a \emph{represented} quantity or
reconstructible from the operands alone (\S\ref{sec:dormant})? \textbf{RQ3}: is the decodable
direction causally used to produce the answer (\S\ref{sec:dormant})?
