\section{Generality and Limitations}
\label{sec:generality}

\paragraph{Replication in matched format, and a format confound.}
In matched bare format the collapse is not specific to Llama-3.1-8B. Among models that clear a
parts floor (C4, C6 $\geq 0.80$), the composed form collapses for Gemma-2-9b-it (C1 $= 0.043$,
C4 $= 0.99$) and Llama-3.2-3B (C1 $= 0.36$), alongside base and instruct Llama-3.1-8B; three
others (Qwen2.5-7B, Mistral-7B, Llama-3.2-1B) fail the parts in bare format and are out of
scope, not counterexamples (we name rather than drop them). Chat formatting changes this, not
cleanly: Gemma-2-9b-it \emph{composes} in its native chat template (C1 $= 0.95$), which would
look like a family dissociation, but there Llama-3.1-8B falls below the parts floor (C4 $= 0.70$)
and leaves scope, so the composing and failing models are never compared in the same format. We
read this as replication in matched bare format plus a prompt-format confound, \emph{not} as
evidence that some families are immune; per-model native-format evaluation is the right axis for
a clean cross-family claim, which we do not make.

\paragraph{Limitations.}
The causal localization is distributed (operand positions matter but no sparse circuit is
recovered), so we characterize \emph{where}, not a minimal mechanism; the operation and depth
controls (A1, A2, D1) are instruct-only; and the zero-excluding gap is small and only in the
harder band, with the dormancy resting on the causal-share certification. None of these affects
the central result.

\paragraph{Conclusion.}
A parenthesized additive identity selectively breaks multiplicative composition in Llama-3.1-8B,
and the tempting reading that the product is represented at the answer site but unused is an
interpretability illusion: the decodable answer-site subspace is operand-dominated and causally
inert, while the answer is re-derived diffusely from the operands. The portable lesson is that a
high decodability $R^2$ needs a baseline and a causal control before it can support any claim
about what a model computes; we release code, data, and the controls so the null and its
positive control can be checked.
